Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
minor

Figure 4 shows a Suricata rule that captures a ping scan implemented
with the NMAP Tool~\cite{netmap}. The relevant options are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

@@

@@

\tname{} is a technique that uses positive and negative examples to
synthesize signature-based \nids\ rules, such as those from Snort and
Suricata. The goal of \tname\ is to create a rule that \emph{only}
captures the positive traffic, \ie{}, the malicious sequence of
messages.

>>>>

Figure 4 shows a Suricata rule that captures a ping scan implemented
with NMAP~\cite{netmap}, a network discovery and security auditing
open-source tool. The relevant options are in bold---the option
\CodeIn{dsize: 0} indicates that the packet has no bytes in the
payload and the option \CodeIn{itype: 8} indicates that the packet to
be captured are ICMP Echo requests.

@@

\tname{} is a technique that uses (1) benign and malicious network
traffic and (2) existing signature-based \nids\ rules to synthesize
new rules. The goal of \tname\ is to create plausible rules that
\emph{only} captures the positive traffic, \ie{}, the malicious
messages.

@@
